Pre/Post-Trikafta

### 2022-01-27 Christine Chan/Pre-post Trikafta/pre_post_trikafta.Rmd
Form Combining
finished CHCO and started Montana, bit of work to be done on montana

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S://PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
}
knitr::opts_knit$set(root.dir = home_dir)
```

```{r}
# Import 
df = read.csv("./Prepost Triakfta/Data_Cleaned/chco_bmi_pft.csv")
```

>>>>

NOTE: I HAVE THE SHARED DRIVE AS S:, to change if mapped to another letter
```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
library(lubridate)
library(stringr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S://PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Christine Chan"
}
knitr::opts_knit$set(root.dir = home_dir)
```

Import the datasets (I'll be doing this one site at a time to look at the variables etc)
```{r data import}
###### Import CHCO data ###########

# bmi, pulm function 577 obs
# 8 vars MRN - ID, date for visits; start - ? start of trt?, fev, bmi, height, weight, fec 
chco_bmi_pft = read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/chco_bmi_pft.csv")

# continuous glucose monitoring, 23 obs
# 105 vars subjectid - number_pre/post for visit and a date; numbers dont seem to correspond to mrn in bmi pft
chco_cgm = read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/chco_cgm.csv")

# chco glycemic, 261 obs
# 7 var MRN and CFF id (=subjectid?), date for visits; start... etc
chco_glycemic = read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/chco_glycemic.csv")

# chco registry 108 obs
# CFF ID and MRN, start date
chco_registry = read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/chco_registry.csv")
###################################

###### IMPORT MONTANA DATA ########

# NEED TO RENAME VARIABLES TO MATCH CHCO#
# bmi, pulm function 975 obs
montana_bmi_pft <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_bmi_pft.csv")

# cgm 16 obs
montana_cgm <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_cgm.csv")

# registry: we need to combine demo (126), genotypes (126), pancreatic (241), gtubes (155)
montana_demo <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_demo.csv")
montana_genotypes <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_genotypes.csv")
montana_gtubes <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_gtubes.csv") # what are the dates here
montana_pancreatic <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_pancreatic.csv") # what is this? just dates and cffid
# ask tim:what do we need to do with gtubes and pancreatic dates? dont look like chco data

# glycemic 279
montana_glycemic_registry <- read_csv("S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/montana_glycemic_registry.csv") # looks identical
###################################

###### IMPORT UW DATA #############
###################################

###### IMPORT ? DATA ########
###################################

```

Lets try and stitch these sets together by site (one site at a time as above)
note: by default, the dplyr join functions join by all variables in common. So we need to make sure the common variables are same format and name
```{r form stitching}
####### CHCO ############
# CGM Data Cleaning
# get a CFF ID and visit variable by splitting subjectid variable into CFF ID and Visit
chco_cgm$`CFF ID` = as.numeric(sub("_.*", "", chco_cgm$subject_id))
chco_cgm$Visit = sub(".*_", "", chco_cgm$subject_id)

# Get a Date variable by taking the date from "date time" char variable date_cgm_placement
# weird because one obs isnt in a date time, just a date so ill just brute it
chco_cgm = chco_cgm %>% mutate(datewithtime = str_detect(date_cgm_placement, " "),
                               Date = ifelse(datewithtime,sub(" .*", "", chco_cgm$date_cgm_placement), date_cgm_placement))

# per tim, its ok to have more than 2 dates per subject,
# as it looks like a lot of this stuff was collected at different times for different subjects;
# i expect this will make it pretty long

chco_long = full_join(chco_glycemic, chco_bmi_pft) # will join by MRN, Start, Date

chco_long = full_join( chco_registry, chco_long) # joins by MRN, CFFID, Start
chco_long = full_join(chco_long, chco_cgm) # joins by cff id and date

# add in a site id variable
chco_long$site = "CHCO"

#########################

####### Montana ############
# to do: registry var differences in name and type
# rename the bmi_pft to chco names
# cgm, glycemic look good

# differences in montana and chco registry vars:
# Race labels
# make registry dataframe
montana_registry = full_join(montana_demo, montana_genotypes)
montana_registry = full_join(montana_registry, montana_pancreatic)
montana_registry = full_join(montana_registry, montana_gtubes)

# CGM looks like this is the same as CHCO (GROOVY)
# cgm data cleaning
montana_cgm$`CFF ID` = as.numeric(sub("_.*", "", montana_cgm$subject_id))
montana_cgm$Visit = sub(".*_", "", montana_cgm$subject_id)

# Get a Date variable by taking the date from "date time" char variable date_cgm_placement
montana_cgm = montana_cgm %>% mutate(datewithtime = str_detect(date_cgm_placement, " "),
                               Date = ifelse(datewithtime,sub(" .*", "", montana_cgm$date_cgm_placement), date_cgm_placement))

#########################

####### UW ############
#########################

####### UM? ############
#########################

```
